---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)

backpack <- CodeClanData::backpack

```


Q1:
Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}
backpack
```

Q2:
What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
backpack %>% 
  ggplot() +
  geom_histogram(aes(x = backpack_weight), fill = "darkgreen", bins = 20) +
  labs(y = "number of backpacks", x = "weight") +
  theme_light()
```

Q3:

Are there differences in backpack weight between sex?

```{r}

backpack %>% 
  ggplot() +
  geom_histogram(aes(x = backpack_weight, fill = sex), bins = 20) +
  facet_wrap(~sex, nrow = 2) +
  labs(y = "number of backpacks", x = "weight") +
  theme_light()

```

Q4:

What is the relationship between body weight and backpack weight?

```{r}
backpack %>% 
  ggplot(aes(x = backpack_weight, y = body_weight)) + 
  geom_point() +
  theme_light()
```

No clear relationship


Q5:

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
backpack %>% 
  ggplot(aes(x = backpack_weight, y = body_weight, colour = sex)) + 
  geom_point() +
  facet_wrap(~sex, nrow = 1) +
  theme_light()

```

Q6:

What proportion of students report back pain?

```{r}
backpack %>% 
  mutate(back_pain = if_else(back_problems == 1, "Yes", "No") %>% 
  ggplot(aes(x = back_problems))+
  geom_col()
  
```

