---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)

project <- read_csv("data/project_management.csv")
```

```{r}
project %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
    geom_abline(
    intercept = model$coefficients[1],
    slope = model$coefficients[2],
    col = "blue"
  )
```

```{r}
project %>% 
  summarise(cor(estimated_length, actual_length))
```
A correlation value of 0.8 shows a strong correlation.


```{r}
model <- lm(formula =  actual_length ~ estimated_length, data = project)

model
```

An increase of 1 unit of estimated length will increase actual length by 1.223 units.

```{r}
summary(model)
```
This is statistically significant

```{r}
library(ggfortify)
plot(model)
```
Residuals v fitted, seems to drift but should be ok


Normals Q-Q, residuals seem to be normally distributed

Scale-Location, values stay within a positive band so no problems

Residuals vs Leverage, all values within the Cook's distance except 1


Ext


```{r}
plot(model) +
geom_text(aes(label = 1:nrow(project)))
```

point 5 is an outlier of high leverage therefore influential
point 18 is an outlier of low leverage so not influential

```{r}
project2 <- project[-18,]
```

```{r}
model2 <- lm(formula = actual_length ~ estimated_length, data = project2)

model2
```

The intercept and estimated_length coefficient change very little

```{r}
project2 %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_abline(
    intercept = model2$coefficients[1],
    slope = model2$coefficients[2],
    col = "red"
  ) +
  geom_abline(
    intercept = model$coefficients[1],
    slope = model$coefficients[2],
    col = "blue"
  )
```

```{r}
project3 <- project[-5, ]
```

```{r}
model3 <- lm(formula = actual_length ~ estimated_length, data = project3)

model3
```
the intercept coefficient has changed a lot and estimated_length by a significant amount


```{r}
project3 %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_abline(
    intercept = model3$coefficients[1],
    slope = model3$coefficients[2],
    col = "red"
  ) +
  geom_abline(
    intercept = model$coefficients[1],
    slope = model$coefficients[2],
    col = "blue"
  )
```

