---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(GGally)

housing <- read_csv("data/housing_prices.csv")
```



ggpairs zooming in too much for all columns

```{r}
ggpairs(housing, columns = 1:5)
```

0.934 correlation very strong

Feature engineering

Use the "raw" dataset to make more meaning with new variables

```{r}
house <- housing %>% 
  mutate(bedrooms_per_house = total_bedrooms / households,
         rooms_per_house = total_rooms / households,
         people_per_house = population / households,
         bedrooms_per_person = total_bedrooms / population,
         rooms_per_person = total_rooms / population,
         bedrooms_per_room = total_bedrooms / total_rooms,
         non_bedrooms_per_houe = rooms_per_house - bedrooms_per_house)

```

Could have used long and lats, join to external data for cities in California

```{r}
housing_trim <- housing %>% 
  select(-total_bedrooms)
```

```{r}
ggpairs1 <- house %>% 
  select(median_house_value, 
         housing_median_age, 
         median_income,
         ocean_proximity) %>% 
  ggpairs()

ggpairs2 <- house %>% 
  select(median_house_value, 
         total_rooms,
         households,
         population,
         people_per_house,
         rooms_per_house, 
         total_bedrooms) %>% 
  ggpairs()

ggpairs2
```


```{r}
housing_trim %>% 
  ggpairs()
```

High correlation between median house price and median income

Strong correlation between median house price and ocean proximity

```{r}
housing_trim %>% 
  ggplot(aes(x = median_income , y = median_house_value)) +
  geom_point()
```

```{r}
housing_trim %>% 
  ggplot(aes(x = ocean_proximity, y = median_house_value)) +
  geom_boxplot()
```

4 dummy variables
<1 hour ocean
near ocean/bay
inland
island




```{r}
lm1 <- lm(median_house_value~ median_income, housing_trim)

summary(lm1)
```

Statistically significant and an ok r squared value

```{r}
library(ggfortify)
autoplot(lm1)
```
Diagnostics have no problems, scale-location shows the values have less heteroskedasticity as median income increases and skewed tails from QQ plot

```{r}
housing_trim %>% 
  distinct(ocean_proximity)
```


```{r}
housing_dummy <- housing_trim %>% 
  mutate(location = case_when(
    ocean_proximity == "<1H OCEAN" ~ "close",
    ocean_proximity == "INLAND" ~ "inland",
    ocean_proximity == "ISLAND" ~ "island",
    TRUE ~ "near"
  )) %>% 
  pivot_wider(names_from = location, values_from = location, names_prefix = "location_") %>% 
  mutate(across(starts_with("location_"), ~if_else(is.na(.x), 0, 1))) %>% 
  select(-location_island)
```


```{r}
lm2 <- lm(median_house_value ~ median_income + ocean_proximity, housing_dummy)

summary(lm2)
```

Statistically significant and good r squared value

>How to know about the dummy variable removed?

```{r}
autoplot(lm2)
```

Diagnostics ok except for some high leverage outliers and less heteroskedasticity as median income increases and right tail skewed from the same outliers

```{r}

lm3 <- lm(median_house_value ~ log(median_income) + ocean_proximity + log(median_income):ocean_proximity, housing_dummy)

summary(lm3)
autoplot(lm3)

```

Much higher r squared value and still statistically significant

```{r}
autoplot(lm3)
```
Diagnostics show that this interaction is not justified


```{r}
housing_trim %>% 
  ggplot(aes(x = median_income, y = median_house_value, colour = ocean_proximity)) +
  geom_smooth(method = "lm", se = FALSE)
```


```{r}

```

