---
title: "R Notebook"
output: html_notebook
---


Loading in dataset and initial investigation.

```{r}
library(tidyverse)

books <- read.csv("2_weekend_homework/data/books.csv")


names(books)
```

```{r}
dim(books)
```
Mixture of chr and int columns.


```{r}
books %>% 
  summarise(
    across(
      .cols = everything(),
      .fns = ~sum(is.na(.x))
    )
  )
```

No missing values in any column.

Q1: Classify books based on their number of pages

```{r}
books %>% 
  select(title, num_pages) %>% 
  mutate(
    book_size = case_when(
      num_pages > 900 ~ "Very Large",
      num_pages > 500 ~ "Large",
      num_pages > 300 ~ "Medium",
      TRUE ~ "Small"
    )
  )
```

Q2: Find the top 10 highest average rating by publisher

```{r}
books %>% 
  select(title, average_rating, publisher) %>% 
  group_by(publisher) %>% 
  summarise(publisher_rating = mean(average_rating)) %>% 
  slice_max(publisher_rating, n = 10)
```

There are 12 publishers with a perfect score of 5

Q3: Order John Grisham books by rating

```{r}
books %>% 
  select(title, authors, average_rating) %>% 
  #used the grepl function to include books co-authored by John Grisham
  filter(grepl("John Grisham", authors)) %>% 
  arrange(desc(average_rating))
  
```

Q4: Determine which authors are considered above average

```{r}
#save the average rating across all books in a variable
average_rating_all <- books %>% 
  summarise(mean(average_rating))

books %>% 
  select(authors, average_rating) %>% 
  group_by(authors) %>% 
  summarise(author_rating = mean(average_rating)) %>% 
  filter(author_rating > pull(average_rating_all))
```


Q5: Check which languages were most popular for the reviewed books

```{r}

#recode different types of english to all be classed as english
recoded_books <- books %>% 
  select(title, language_code) %>% 
  mutate(language_code = 
    if_else(
      language_code %in% c("en-US", "en-CA", "en-GB"),
      "eng",
      language_code)
  )
  

recoded_books %>% 
  select(title, language_code) %>% 
  group_by(language_code) %>% 
  summarise(occurences = n()) %>% 
  arrange(desc(occurences))
```



