---
title: "R Notebook"
output: html_notebook
---


```{r}
library(CodeClanData)
library(tidyverse)
library(ggplot2)


qb_revenue_breakdown
```

1) Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
qb_revenue_breakdown %>% 
  ggplot(aes(x = Product, y = Revenue, fill = Year)) +
  geom_col() +
  theme

``` 















2: 
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).


```{r}
qb_monthly_sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot(aes(x = Date, y = Amount)) +
  geom_line() + 
  theme
```
3:
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
qb_monthly_sales %>% 
  filter(Cashflow == "Total Revenue" | Cashflow == "Cost") %>% 
  ggplot(aes(x = Date, y = Amount, group = Cashflow)) +
  geom_line(aes(colour = Cashflow)) +
  theme
```
Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

```{r}
qb_competitors %>% 
  ggplot(aes(x = Year, y = Revenue, group = Company)) +
  geom_area(aes(fill = Company)) +
  theme 
```

Question 5.
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
qb_competitors %>% 
  ggplot(aes(x = Year, y = Revenue, group = Company)) +
  geom_line(aes(colour = Company)) + 
  geom_point() +
  theme
  


```


Question 6.
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.

```{r}
qb_device_data %>% 
  mutate(time = hours + mins/60) %>% 
  ggplot(aes(x = time, y = counts, colour = device)) +
  geom_line() +
  facet_wrap(id~device) +
  custom_theme
  
```



```{r}
custom_theme <- theme(panel.background = element_rect(fill = "white"),
                      panel.grid = element_line(colour = "grey92"),
                      axis.text = element_text(size = 8),
                      axis.title = element_text(size = 10),
                      title = element_text(size = 12))


col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

theme <- list(custom_theme, scale_colour_manual(values = col_scheme))

```

