---
title: "R Notebook"
output: html_notebook
---

Q1: Read in the data, returned a list of lists so had to access the first 
element which was the data frame

```{r}
meteor_data <- source("meteors_clean.R")
meteor_data <- meteor_data[[1]]


```


Q2: Top 10 biggest meteors names and year
```{r}
meteor_data %>% 
  slice_max(`mass(g)`, n = 10) %>% 
  select(name, year)
```

Q3:

```{r}
meteor_data %>% 
  group_by(fall) %>% 
  summarise(average_mass = mean(`mass(g)`))
```

Q4:

```{r}
meteor_data %>% 
  filter(year >= 2000) %>% 
  group_by(year) %>% 
  summarise(num_meteors = n())
  
```

Q5:

```{r}
get_meteorite_count <- function(df, input_year){
  
  number_of_meteors <- df %>% 
    filter(year == input_year) %>% 
    summarise(num_meteors = n()) %>% 
    pull()
  
  if (number_of_meteors > 0){
    return(paste("In", input_year, ", there were", number_of_meteors, "meteorites."))
  }
  if (number_of_meteors == 0){
    return(paste("As far as we know, there were no meteorites that year"))
  }
}


```

Q6: The function could be improved by including errors for incorrect datatypes in each argument. A range of years could also be included to cover only years with recorded data. The data frame could be checked also to make sure it includes the correct columns

Q7:

```{r}
library(testthat)

test_that("Non numeric inputs return an error", {
  expect_error(get_meteorite_count(meteor_data, TRUE))
  expect_error(get_meteorite_count(meteor_data, "Hello"))
})
```
Q8:

```{r}
refactor_get_meteorite_count <- function(df, input_year){
  
  if (!is.numeric(input_year)){
    stop("Non-numeric input")
  }
  
  number_of_meteors <- df %>% 
    filter(year == input_year) %>% 
    summarise(num_meteors = n()) %>% 
    pull()
  
  if (number_of_meteors > 0){
    return(paste("In", input_year, ", there were", number_of_meteors, "meteorites."))
  }
  if (number_of_meteors == 0){
    return(paste("As far as we know, there were no meteorites that year"))
  }
}
```


```{r}
library(testthat)

test_that("Non numeric inputs return an error", {
  expect_error(refactor_get_meteorite_count(meteor_data, TRUE))
  expect_error(refactor_get_meteorite_count(meteor_data, "Hello"))
})
```

