---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
sleep <- data(msleep)

sleep <- msleep
```
Q1:

alpha  = 0.05
h0 = mean_sleep_total - 7 = 0
hA = mean_sleep_total - 7 != 0

```{r}
sleep_stat <- sleep %>% 
  summarise(mean = mean(sleep_total))

```


```{r}
null_distribution <- sleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")
```



```{r}
null_distribution %>% 
  visualise(bins = 30) +
  shade_p_value(obs_stat = sleep_stat$mean, direction = "both")
```
```{r}
null_distribution %>% 
  get_p_value(obs_stat = sleep_stat$mean, direction = "both") 
```

p-value close to 0 means we can reject our null hypothesis and confirm that the
mean sleep time of animals in the dataset differs statistically significantly 
from the 7 hours of jabberwockies


Q2:

alpha = 0.05
h0 = mean_omni_sleep - mean_herb_sleep = 0
hA = mean_omni_sleep - mean_herb_sleep > 0

Independent samples so combine the rows

```{r}
omni_and_herbi <- sleep %>% 
  filter(vore == "omni" | vore == "herbi") %>% 
  select(c(sleep_total, vore))
```

Create null distribution, swap labels

```{r}
null_distribution_vore <- omni_and_herbi %>% 
  specify(sleep_total ~ vore) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))
```


Observed stat using infer

```{r}
observed_stat_vore <- omni_and_herbi %>% 
  specify(sleep_total~vore) %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))
```

Visualise and calculate p value

```{r}
null_distribution_vore %>% 
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat_vore, direction = "greater")
```

```{r}
null_distribution_vore %>% 
  get_p_value(obs_stat = observed_stat_vore, direction = "greater")
```
p-value of 0.106 > 0.05 alpha value so we fail to reject the null hypothesis. 
Can't say that the mean sleep time of omnivores is statistically, significantly
greater than herbivores.

Q3:

 Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.
 
 alpha = 0.05
 h0 = prop_domestic - 0.05 = 0
 hA = prop_domestic - 0.05 > 0
 
```{r}
dom <- sleep %>% 
  filter(!is.na(conservation)) %>% 
  mutate(is_domesticated = if_else(conservation == "domesticated", TRUE, FALSE))
  
observed_stat_dom <- dom %>% 
  specify(response = is_domesticated, success = "TRUE") %>% 
  calculate(stat = "prop")
```
 
 
```{r}
null_distribution_dom <- dom %>% 
  specify(response = is_domesticated, success = "TRUE") %>% 
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 5000, type = "draw") %>% 
  calculate(stat = "prop")
```


null distribution looks strange

```{r}
null_distribution_dom %>% 
  visualise(bins = 10) +
  shade_p_value(obs_stat = observed_stat_dom, direction = "greater")
```
```{r}
null_distribution_dom %>% 
  get_p_value(obs_stat = observed_stat_dom, direction = "greater")
```
 
 p-value 6e-04 much smaller than 0.05 alpha so we can reject the null hypothesis
 and state that the proportion of domesticated animals is greater than 5%
 
 
 >1.2
 
 Q1:
 
 One sample proportion test
 h0: prop_known - 0.4 = 0   
 
 The proportion of people who know the coffee shop is 40%
 
 hA: prop_known - 0.4 > 0 
  
 The proportion of people who know the coffee shop is greater than 40%
 
 alpha = 0.05
 
 Draw method
 
 Q2:
 
 Two sample proportion test
 
 h0: B_click_prop - A_click_prop = 0
 
Users aren't more likely to click the banner if it's positioned at the top of 
the page

hA: B_click_prop - A_click_prop > 0

Users are more likely to click the banner if it's positioned at the top of 
the page

alpha = 0.05

Permute method

Q3:

One sample mean test

h0: mean_width = 145

The mean width is 145mm

hA: mean_width != 145

The mean width is significantly different from 145mm

alpha = 0.01

bootstrap method

>1.3

Q1:

p-value 0.07 > 0.05 alpha so we fail to reject the null hypothesis.
Number of people who know the coffee shop is likely 40% or less.

Q2:

p-value 0.006 < 0.01 alpha so we reject the null hypothesis.
Users are more likely to click the banner if it's positioned at the top of 
the page


Q3:
p-value 0.55 > 0.05 alpha so we fail to reject the null hypothesis. 
The mean width isn't significantly different from 145mm, no drift.





```{r}
library(tidyverse)
transactions <- read_csv("data/online_retail_subset.csv")
```

```{r}
num_a <- transactions %>% 
  filter(StockCode == 22469) %>% 
  nrow()

num_b <- transactions %>% 
  filter(StockCode == 21110) %>% 
  nrow()

support_a <- num_a / nrow(transactions)

support_b <- num_b / nrow(transactions)

support_ab <- (num_a + num_b) / nrow(transactions)

conf_ab <- support_ab / support_a

lift_ab <- support_ab / (support_a * support_b)
```



```{r}
library(arules)
library(arulesViz)
```
```{r}
transactions_reformat <- transactions %>%
  select(InvoiceNo, Description) %>%
  na.omit()

write_csv(transactions_reformat, "transactions_reformat.csv")

apriori_format <- read.transactions("transactions_reformat.csv", format = "single", sep = ",", header = TRUE, cols = c("InvoiceNo", "Description"))
```

```{r}
rules <- apriori(transactions_reformat, parameter = list(supp = 0.001, conf = 0.8))

options(digits = 2)
rules
```
 
 